\problemname{Reduplication}
\noindent

Reduplication is when one repeats a word several times, often to reinforce or alter its meaning.
In some languages, such as Indonesian, reduplication is very common and
serves various grammatical functions. Even in Swedish, reduplication is used
occasionally, for example, saying \texttt{"hej hej"} instead of just \texttt{"hej"}.

Rama is a diligent user of reduplication when chatting with his friends. He sometimes
writes the same word up to nine times, which takes a long time. Therefore, he usually
writes the word once, followed by a number indicating how many times the word should
be repeated.

Write a program that reads in a word Rama intends to repeat and how many times it
should be repeated. The program should then print the word repeated the correct number of times.

\section*{Input}
The first line of the input contains a string $s$ ($2 \leq |s| \leq 10$), the word Rama wants to write.
The word consists of letters from \texttt{a}-\texttt{z}.

The next line contains a digit between $1$ and $9$, the number of times Rama wants to write the word.

\section*{Output}
Print $s$ as many times as the digit indicates. 

\section*{Points}
Your solution will be tested on several test case groups.
To get the points for a group, it must pass all the test cases in the group.

\noindent
\begin{tabular}{| l | l | p{12cm} |}
  \hline
  \textbf{Group} & \textbf{Point value} & \textbf{Constraints} \\ \hline
  $1$    & $20$       & The digit is $1$. \\ \hline
  $2$    & $80$       & No additional constraints. \\ \hline
\end{tabular}
