\problemname{Three in a Row}
\noindent

The mathematician Lenore Oljer has done so much math that she has grown tired of prime numbers.
She has now started studying so-called ``nice triplets''. It's very easy to create a nice
triplet. Start with an integer $a$ greater than zero and then create the triplet
$(a, a+1, a+2)$. All triplets created in this way are considered nice. Some examples of
nice triplets are $(4,5,6)$ and $(15,16,17)$.

To learn more about nice triplets, Lenore wants to find out how many numbers can be
written as the product of all the numbers in a nice triplet. She calls these numbers
``triple numbers''. Some examples of triple numbers are $24=2 \cdot 3 \cdot 4$
and $336 = 6 \cdot 7 \cdot 8$. Lenore now wants to know how many triple numbers
there are that are less than the given number $N$.

Write a program that takes the number $N$ as input and prints out how many numbers
less than $N$ that are triple numbers.

\section*{Input}
The first and only line of the input contains the integer $N$ ($1 \le N \le 10^9$),
whose meaning is described above.

\section*{Output}
Print an integer: the number of integers less than $N$ that are triple numbers. 

\section*{Points}
Your solution will be tested on several test case groups.
To get the points for a group, it must pass all the test cases in the group.

\noindent
\begin{tabular}{| l | l | p{12cm} |}
  \hline
  \textbf{Group} & \textbf{Point value} & \textbf{Constraints} \\ \hline
  $1$    & $20$       & $N \leq 30$ \\ \hline
  $2$    & $20$       & $N \leq 80$ \\ \hline
  $3$    & $20$       & $N \leq 1000$ \\ \hline
  $4$    & $20$       & $N \leq 10^5$ \\ \hline
  $5$    & $20$       & No additional constraints. \\ \hline
\end{tabular}
