\problemname{Segment Monitoring}

\noindent
After successfully conquering all city-states in Kattago, the super-feline kingdom of 
Katen and its leader Kattis seek better control over their conquered city-states, particularly in the state of Segby. 
Segby consists of a single long line. Recently, rumors of rebellion have surfaced, 
something that will not be tolerated. More specifically, they have identified that all suspicious houses 
lie between $x_{min}$ and $x_{max}$, meaning the suspected houses are points $x$ on the number line that 
satisfy $x_{min} \le x \le x_{max}$.

\illustration{0.35}{kattIsWatching}{Kattis is watching.}

To avoid a cat-astrophe, Kattis has asked the company Purrfect Segments Inc. to manufacture 
different cameras that can monitor the entire street between $x_{min}$ and $x_{max}$ 
(Kattis herself has realized the importance of surveillance after several attempts to attack a well-monitored wall).

Purrfect Segments Inc. installs their cameras at specific paw-sitions so that each camera 
has a unique serial number $s$, where camera $s$ can monitor a segment $[a_s,b_s]$ to purr-fection. 
This means that the camera $s$ monitors all numbers $x$ on the number line such that $a_s \le x \le b_s$.

The only problem is that the cameras are often vandalized since they closely resemble speed cameras. 
When a camera is vandalized, it can no longer monitor its segment. To keep track of the suspected segment, 
they will constantly need to install new cameras.

Purrfect Segments Inc. now seeks your help for the next $Q$ days. Initially, there are no cameras 
monitoring the street at all. Each morning, either a camera will be installed, or one will be vandalized. 
As they want to appear even more efficient than the Lund municipality (see \textit{Illuminated City}), 
they never want to activate more than two cameras in a single day.

You are given information about which cameras will be installed and vandalized over the next $Q$ days. 
Your task is to determine, for each day, whether it is possible to monitor the entire segment $[x_{min}, x_{max}]$ 
by activating only one or two cameras. Note that at the beginning of each day, no camera is activated.


\section*{Input}
The first line of the input contains the integers $x_{min}$ and $x_{max}$ ($1 \leq x_{min} < x_{max} \leq 10^9$), 
representing the segment where the suspected houses are located.

The second line contains the integer $Q$ ($1 \le Q \le 2 \cdot 10^5$), 
indicating the number of days in the test case.

The following $Q$ lines start with either ``+'' if a camera is to be installed, or ``-'' if a camera has been vandalized:
\begin{itemize}
  \item ``+'': The line contains $3$ integers, $s$, $a$, and $b$ ($1\le s \le 10^6$, $0\le a < b \le 10^9$), 
  indicating that a camera with serial number $s$ has been installed to monitor the segment $[a,b]$.
  \item ``-'': The line contains the integer $s$, the serial number of the camera $s$ that has been vandalized.
  It is guaranteed that the vandalized camera was installed.
\end{itemize}

All cameras have unique serial numbers and are not activated when installed.

\section*{Output}
Print $Q$ lines, where the $i$-th line is the answer for the $i$-th day.
\begin{itemize}
  \item If the segment with the suspicious houses can be monitored with $1$ camera, print $1$.
  \item If it is not possible to monitor with $1$ camera but is possible with $2$, print $2$.
  \item Otherwise, print $-1$.
\end{itemize}


\section*{Points}
Your solution will be tested on several test case groups.
To get the points for a group, it must pass all the test cases in the group.

\noindent
\begin{tabular}{| l | l | p{12cm} |}
  \hline
  \textbf{Group} & \textbf{Point value} & \textbf{Constraints} \\ \hline
  $1$    & $10$       & $Q \le 2$ \\ \hline
  $2$    & $10$       & The answer is either $1$ or $-1$. \\ \hline
  $3$    & $20$       & $Q \le 100$ \\ \hline
  $4$    & $25$       & $Q \le 1000$ \\ \hline
  $5$    & $35$       & No additional constraints. \\ \hline
\end{tabular}

\section*{Explanation of sample 1}
On the first day, camera with serial number ``1'' was installed on the segment $[2,3]$.
There is no way to monitor the entire segment $[2,6]$ by activating any cameras, so the answer for the first day is ``-1''.

On the second day, camera with serial number ``2'' was installed on the segment $[4,6]$.
There is still no way to monitor the entire segment, since it activating cameras ``1'' and ``2'' would leave the segment between 3 and 4 unmonitored.
Therefore, the answer for the second day is ``-1''.

On the third day, camera with serial number ``2'' was vandalized.
There is still no way to monitor the entire segment $[2,6]$, so the answer for the third day is ``-1''.

On the fourth day, camera with serial number ``3'' was installed.
By activating cameras ``1'' and ``3'' the segment $[2,7]$ is monitored, including the suspicious segment $[2,6]$.
Since there is no way to monitor $[2,6]$ by activating only 1 camera, the answer for the fourth day is ``2''.


\section*{Explanation of sample 3}
On the first day, camera with serial number ``123'' was installed on the segment $[10,15]$.
There is no way to monitor the entire segment $[10,20]$ by activating any cameras, so the answer for the first day is ``-1''.

On the second day, camera with serial number ``234'' was installed.
By activating cameras ``123'' and ``234'', the entire suspicious segment $[10,20]$ is monitored.
Therefore, the answer for the second day is ``2''.

On the third day, camera with serial number ``345'' was installed.
By activating only camera ``345'', the entire suspicious segment $[10,20]$ is monitored.
Therefore, the answer for the third day is ``1''.
