\problemname{Long Bus Trip}
\noindent
The travelling pillow round the neck, headphones on, and the music turned up to the highest volume.
Now everyone is ready for the long bus journey down to the wonderful "Sunset Valley"!

But oh no! Everyone on the bus seems to have forgotten to bring water,
and they will become extremely thirsty during the long bus journey.
But luckily, you own the bus company,
and you have installed a water tank that all passengers and the driver can drink from.

The bus starts moving at second $0$, and arrives at "Sunset Valley" at second $X$.
During the journey, there are $N$ water stations where the bus's water tank can be filled.
The bus will be at the $i$-th water station $(1 \leq i \leq N)$ at second $S_i$.

Initially, there is no water in the water tank, but there is also a water station where the bus starts.
The cost to fill the water tank is $W$ SEK per liter, regardless of which station the water is filled from.
We also assume that the time to fill the water tank is negligible.

Initially, all $M$ passengers are on the bus. Passengers are indexed from $1$ to $M$.
The $j$-th passenger $(1 \leq j \leq M)$ needs $1$ liter of water at second $D_j$.
If the passenger has drunk water, they will need to drink water again after $T$ seconds.
Thus, passenger $j$ will need 1 liter of water at times $D_j + k\cdot T$ $(k = 0,1,2,\ldots)$.
Note that $T$ will be the same for all passengers.

If the water tank is empty when a passenger needs water, the passenger will demand to get off the bus.
If the passenger leaves before reaching "Sunset Valley", you must refund their bus ticket,
which costs $C_j$ SEK.

The driver also needs to drink water and requires it at seconds $k\cdot T$ $(k = 0,1,2,\ldots)$.
If the water tank is empty when the driver wants water, the bus will stop running, and no one will be able to go to "Sunset Valley".

No two passengers will need water at the same time. When the bus arrives at a water station, neither passengers nor the driver will need water.

By determining how much water is filled in the water tank, we want to minimize the sum of the costs from water and refunds, 
while still being able to drive to "Sunset Valley". Can you calculate the minimum amount of money you can spend and still be able to go there?


\section*{Input}
\noindent
The first line contains the integers $X$, $N$, $M$, $W$, and $T$ 
($1 \leq T \leq X \leq 10^{12}, 1 \leq N,M \leq 2\cdot 10^5, 1 \leq W \leq 10^6$). 
These represent that the bus will arrive at the destination at second $X$, there are $N$ water stations, 
$M$ passengers on the bus, the cost of water is $W$ SEK per liter, and the time interval 
for all passengers and the driver to require water will be $T$ seconds.

Then follows $N$ lines, where the $i$-th ($1 \leq i \leq N$) line contains an integer $S_i$ $(1 \leq S_i \leq X-1)$, 
the second at which the bus will arrive at the $i$-th water station.

The next $M$ lines contain the integers $D_j$ and $C_j$ ($1 \leq D_j \leq T-1$, $1 \leq C_i \leq 10^9$), 
representing that the $j$th passenger will first require water at second $D_j$, and the cost to refund the $j$-th passenger is $C_j$.

\section*{Output}
\noindent
Print an integer: the minimum cost to be able to drive the bus to "Sunset Valley".

\section*{Scoring}
Your solution will be tested on a set of test groups, each worth a number of points. 
Each test group contains a set of test cases. 
To get the points for a test group you need to solve all test cases in the test group.

\noindent
\begin{tabular}{| l | l | p{12cm} |}
  \hline
  \textbf{Group} & \textbf{Point value} & \textbf{Constraints} \\ \hline
  $1$    & $16$         & $N,M \leq 8$  \\ \hline
  $2$    & $30$         & $N,M \leq 100$ \\ \hline
  $3$    & $24$         & $N,M \leq 2000$ \\ \hline
  $4$    & $30$         & No additional constraints. \\ \hline
\end{tabular}



\section*{Explanation of sample 1:}
If we fill the water tank with 7 liters of water before we start driving, and then add 4 liters at the first water station, we get the following events:

\begin{itemize}
  \item The bus starts moving with 7 liters of water.
  \item The driver, passenger 1, 2, 3, and 4 drink 1 liter of water each at seconds 0, 1, 2, 4, and 6 respectively. Now the bus has only 2 liters of water left.
  \item The driver and passenger 1 drink 1 liter of water each at seconds 7 and 8. Now there is 0 liters of water left.
  \item At second 9, passenger 2 wants to drink water, but there is none left. Therefore, passenger 2 leaves.
  \item At second 10, the water tank is filled with 4 liters of water, as we are at the first water station. Now there are 4 liters of water in the tank.
  \item Passengers 3, 4, the driver, and passenger 1 drink 1 liter each at seconds 11, 13, 14, and 15. Now there are 0 liters of water left.
  \item At second 18, passenger 3 wants water, but there is none. Therefore, passenger 3 leaves.
  \item At second 19, the bus arrives at the destination.
\end{itemize}

A total of 11 liters of water were bought, costing 88 SEK. Only passengers 2 and 3 left and demanded a refund, costing 15 SEK. We pay a total of 103 SEK.

It is impossible to get to "Sunset Valley" for less than 103 SEK.